---
title: "Addressing Maria's Comments"
author: "Casey Schmidt"
date: "2023-12-17"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(tidyr)
library(gtsummary)
library(nlme)
library(car)
library(ggplot2)
library(knitr)
library(univOutl)
library(Matrix)
```

# Creating table 1 
```{r}
fantasy = read.csv("fantasyFootball.csv")

fantasy %>%
  select(Age, FantPos, Division) %>%
  tbl_summary()
```

# Diagnostics 
## Normality of the residuals

```{r}
fantasy$Agesquared <- (fantasy$Age.Centered)^2
fantasy$AgeKnotsquared <- (fantasy$AgeKnot.Centered)^2
fantasy$logPerformance <- log(fantasy$Performance + 5.3)

# With position
modelFantasy_final = lme(logPerformance ~ Age.Centered + AgeKnot.Centered + Rk + FantPos + Division + Age.Centered*FantPos + AgeKnot.Centered*FantPos, 
                   data = fantasy, 
                   random = ~1 + Age.Centered | PlayerID)

png("QQplotALL.png")
#qqnorm(mResAll)

dev.off()
#qqPlot(mResAll)

# RB only
fantasy_rb <- fantasy %>% filter(FantPos == "RB")
modelFantasy_rbFinal = lme(logPerformance ~ Age.Centered + AgeKnot.Centered + Rk + Division, 
                      data = fantasy_rb, 
                      random = ~1 + Age.Centered | PlayerID)

summary(modelFantasy_rbFinal)

mResRB = modelFantasy_rbFinal$residuals

png("QQplots.png")
par(mfrow = c(1,2))
#car::qqPlot(mResAll, ylab = "Sample Quantiles (All positions)")
car::qqPlot(mResRB, ylab = "Sample Quantiles (Running backs)")
dev.off()

# Outliers 
fantasy_nooutl <- fantasy[-boxB(fantasy$Performance)$outliers,]

modelFantasy_nooutl = lme(logPerformance ~ Age.Centered + AgeKnot.Centered + Rk + FantPos + Division + Age.Centered*FantPos + AgeKnot.Centered*FantPos, 
                   data = fantasy_nooutl, 
                   random = ~1 + Age.Centered | PlayerID) 

mResAll_noOutl = modelFantasy_nooutl$residuals
car::qqPlot(mResAll_noOutl)

# Outlier RB
fantasy_rb_nooutl <- fantasy_nooutl %>% filter(FantPos == "RB")

modelFantasy_rb_nooutl = lme(logPerformance ~ Age.Centered + AgeKnot.Centered + Rk + Division, 
                   data = fantasy_rb_nooutl, 
                   random = ~1 + Age.Centered | PlayerID)

mResRB_noOutl = modelFantasy_rb_nooutl$residuals
car::qqPlot(mResRB_noOutl)
```

## Mutlicolinearity 

```{r}
modelVIFall = lme(logPerformance ~ Age.Centered + AgeKnot.Centered + Rk + FantPos + Division, 
                   data = fantasy, 
                   random = ~1 + Age.Centered | PlayerID) 
VIFall = vif(modelVIFall)
vif(modelVIFall)
kable(VIFall)
```

# Cholesky demcomposition for transformed residuals
WITH THE FULL DATA SET
Need to extract the estimated variance covariance matrix of the residuals
doing the thing for all players:
```{r}
#this takes a long time to run dont do it twice
library(Matrix)
library(stats)
mat <-diag(rep(sigma(modelFantasy_final)^2,nobs(modelFantasy_final)))
Linv <- t(solve(chol(mat)))
res <- residuals(modelFantasy_final)
rstar <- Linv %*% res
qqPlot(rstar)
mahalanobis_dist <- t(rstar) %*% rstar
hist(res, breaks = 20, freq=T, ylim=c(0,1000))
hist(rstar, breaks = 20, freq=T, ylim=c(0,1000))
mahalanobis_dist
```
Doing the thing for only running backs
```{r}
mat <-diag(rep(sigma(modelFantasy_rb)^2,nobs(modelFantasy_rb)))
Linv <- t(solve(chol(mat)))
res <- residuals(modelFantasy_rb)
rstar1 <- Linv %*% res
qqPlot(rstar)
mahalanobis_dist <- t(rstar) %*% rstar
hist(res, breaks = 20, freq=T, ylim=c(0,1000))
hist(rstar, breaks = 20, freq=T, ylim=c(0,1000))
mahalanobis_dist
```

```{r}
png("QQplots1.png")
par(mfrow = c(1,2))
car::qqPlot(rstar, ylab = "Transformed Residuals (All positions)")
car::qqPlot(rstar1, ylab = "Transformed Residuals (Running backs)")
dev.off()
```



WITH REMOVED OUTLIERS
# Cholesky demcomposition for transformed residuals
Need to extract the estimated variance covariance matrix of the residuals
doing the thing for all players:
```{r}
#this takes a long time to run dont do it twice
library(Matrix)
library(stats)
mat <-diag(rep(sigma(modelFantasy_nooutl)^2,nobs(modelFantasy_nooutl)))
Linv <- t(solve(chol(mat)))
res <- residuals(modelFantasy_nooutl)
rstar <- Linv %*% res
qqPlot(rstar)
mahalanobis_dist <- t(rstar) %*% rstar
hist(res, breaks = 20, freq=T, ylim=c(0,1000))
hist(rstar, breaks = 20, freq=T, ylim=c(0,1000))
mahalanobis_dist
```
Doing the thing for only running backs
```{r}
mat <-diag(rep(sigma(modelFantasy_rb_nooutl)^2,nobs(modelFantasy_rb_nooutl)))
Linv <- t(solve(chol(mat)))
res <- residuals(modelFantasy_rb_nooutl)
rstar1 <- Linv %*% res
qqPlot(rstar)
mahalanobis_dist <- t(rstar) %*% rstar
hist(res, breaks = 20, freq=T, ylim=c(0,1000))
hist(rstar, breaks = 20, freq=T, ylim=c(0,1000))
mahalanobis_dist
```

```{r}
png("QQplots2.png")
par(mfrow = c(1,2))
car::qqPlot(rstar, ylab = "Transformed Residuals (All positions)")
car::qqPlot(rstar1, ylab = "Transformed Residuals (Running backs)")
dev.off()
```













