

Creating data set with no outliers:
```{r}
#install.packages("univOutl")
library(univOutl)
fantasy = read.csv("fantasyFootball.csv")
fantasy_nooutl <- fantasy[-boxB(fantasy$Performance)$outliers,]
fantasy_nooutl$occassion = fantasy_nooutl$Year - 2016
fantasy_nooutl$Agesquared <- (fantasy_nooutl$Age)^2
fantasy_nooutl$AgeKnotsquared <- (fantasy_nooutl$AgeKnot.Centered)^2
fantasy_nooutl$logPerformance <- log(fantasy_nooutl$Performance + 5.3)
```

Running same models as before but on new data:

First analysis, all players, no outliers

```{r}
model1_nooutl <- lme(logPerformance ~ Age.Centered + Agesquared + AgeKnot.Centered + AgeKnotsquared,
              data = fantasy_nooutl,
              random = ~1 + Age.Centered | PlayerID)
summary(model1_nooutl)
```

Model without squared terms:

```{r}
model2_nooutl <- lme(logPerformance ~ Age.Centered + AgeKnot.Centered,
              data = fantasy_nooutl,
              random = ~1 + Age.Centered | PlayerID)
summary(model2_nooutl)
anova(model1_nooutl, model2_nooutl)
```

Second analysis, all players, no outliers, adjusted model

```{r}
modelFantasy1_nooutl = lme(logPerformance ~ Age.Centered + Agesquared + AgeKnot.Centered + AgeKnotsquared + Rk + FantPos + Division + Age.Centered*FantPos + AgeKnot.Centered*FantPos, 
                    data = fantasy_nooutl, random = ~1 + Age.Centered | PlayerID) 
```

Final model without squared terms
```{r}
modelFantasy_nooutl = lme(logPerformance ~ Age.Centered + AgeKnot.Centered + Rk + FantPos + Division + Age.Centered*FantPos + AgeKnot.Centered*FantPos, 
                   data = fantasy_nooutl, 
                   random = ~1 + Age.Centered | PlayerID) 

summary(modelFantasy_nooutl)
anova(modelFantasy1_nooutl, modelFantasy_nooutl)
anova(modelFantasy_nooutl)
```









Creating running back only data

```{r}
fantasy_rb_nooutl <- fantasy_nooutl %>% filter(FantPos == "RB")
```

first model: only running backs, unadjusted

```{r}
model1_rb_nooutl <- lme(logPerformance ~ Age.Centered + Agesquared + AgeKnot.Centered + AgeKnotsquared,
              data = fantasy_rb_nooutl,
              random = ~1 + Age | PlayerID)
summary(model1_rb_nooutl)
```

Model without squared terms and anova

```{r}
model2_rb_nooutl <- lme(logPerformance ~ Age.Centered + AgeKnot.Centered,
              data = fantasy_rb_nooutl,
              random = ~1 + Age.Centered | PlayerID)
summary(model2_rb_nooutl)
anova(model1_rb_nooutl, model2_rb_nooutl)
```

Second analysis, running backs only, adjuated model, no outliers

```{r}
modelFantasy1_rb_nooutl = lme(logPerformance ~ Age.Centered + Agesquared + AgeKnot.Centered + AgeKnotsquared + Rk + Division, 
                    data = fantasy_rb_nooutl, 
                    random = ~1 + Age.Centered | PlayerID) 
summary(modelFantasy1_rb_nooutl)
```

Final model without squared terms

```{r}
modelFantasy_rb_nooutl = lme(logPerformance ~ Age.Centered + AgeKnot.Centered + Rk + Division, 
                   data = fantasy_rb_nooutl, 
                   random = ~1 + Age.Centered | PlayerID)
summary(modelFantasy_rb_nooutl)
anova(modelFantasy1_rb_nooutl, modelFantasy_rb_nooutl)
anova(modelFantasy_rb_nooutl)
```




















